---
title: "chartjs - A Chart.js implementation in R"
---

***

chartjs is an implementation of the popular JavaScript vizualisation library [**Chart.js**](www.chartjs.org).

## Installation

The package can be installed from GitHub *via* the **devtools** package: 

```{r Install, eval=FALSE}
devtools::install_github("tutuchan/chartjs", ref = "dev")
```


## Charts

The 6 charts types available in **Chart.js** are implemented : 

+ bar charts,
+ line charts,
+ pie charts,
+ doughnut charts,
+ radar charts,
+ polar area charts

## Features

### Colors

Base colors imported from the Paired palette of [ColorBrewer](http://www.colorbrewer2.org) are available by default. It allows having a light color to represent the data which turns into a stronger color when highlighted.

```{r Colors, echo=FALSE, fig.height=4, fig.width = 15}
RColorBrewer::display.brewer.pal(12, "Paired")
```


### Legends

The 2.0.0 version of Chart.js natively supports legends. Use `cjsLegend` to draw and customize them.

### Scales

As of version 0.2.1, scales can be customized (see the [Chart.js documentation](http://nnnick.github.io/Chart.js/docs-v2/#scales) for a full list of options).


## Acknowledgments

Many thanks to : 

+ the RStudio team and Ramnath Vaidyanathan for the [htmlwidgets](http://www.htmlwidgets.org/) framework,
+ Nick Downie for the [Chart.js](http://www.chartjs.org) library